# Constrained Area vs. Treated Area

```{r, include=FALSE, warning=F, message=F}
# knit options
knitr::opts_chunk$set(
  echo = TRUE
  , warning = FALSE
  , message = FALSE
  , results='hide'
  , fig.width = 10
  , fig.height = 7
)
# bread-and-butter
library(tidyverse)
library(lubridate)
library(viridis)
library(scales)
library(latex2exp)
# visualization
library(kableExtra)
library(cowplot)
library(RColorBrewer)
library(mapview) #Interactive maps
library(leafpop) #map html popup
# spatial analysis
library(sf)
library(USAboundaries)
library(nhdplusTools) # watershed boundaries
library(googlesheets4) # googlesheets4
# set seed
set.seed(11)
```

```{r, results='hide'}
# turn off the s2 processing 
## https://stackoverflow.com/questions/68478179/how-to-resolve-spherical-geometry-failures-when-joining-spatial-data
sf::sf_use_s2(FALSE)
```

## Read in Constraint and AOI Bounds

This data was created in this [prior section](#wf_read_sw) and this [prior section](#wflndscp).

```{r const-rd_dta, results='hide'}
# constraint by ftr, huc12
constrained_byftr_huc12_wide_sf <- sf::st_read("../data/constrained_byftr_huc12_wide_sf.gpkg") |> 
  dplyr::mutate(
      cnstrnt_class = factor(
        cnstrnt_class 
        , levels = c("high constraint", "med. constraint", "low constraint")
        , labels = c("high constraint", "med. constraint", "low constraint")
        , ordered = T
      ) |> forcats::fct_rev()
      , rmn_cnstrnt_class = factor(
        rmn_cnstrnt_class 
        , levels = c("0–15% treatable", "16–35% treatable", ">35% treatable")
        , labels = c("0–15% treatable", "16–35% treatable", ">35% treatable")
        , ordered = T
      ) |> forcats::fct_rev()
    )
#rename sf geom column
  names(constrained_byftr_huc12_wide_sf)[names(constrained_byftr_huc12_wide_sf)==tolower(attr(constrained_byftr_huc12_wide_sf, "sf_column"))] = "geometry"
  sf::st_geometry(constrained_byftr_huc12_wide_sf) = "geometry"
# set crs
transform_crs <- sf::st_crs(constrained_byftr_huc12_wide_sf)
# constraint by wf landscape
constrained_by_wflndscp_wide_sf <- sf::st_read("../data/constrained_by_wflndscp_wide_sf.gpkg") |> 
  sf::st_transform(transform_crs)
#rename sf geom column
  names(constrained_by_wflndscp_wide_sf)[names(constrained_by_wflndscp_wide_sf)==tolower(attr(constrained_by_wflndscp_wide_sf, "sf_column"))] = "geometry"
  sf::st_geometry(constrained_by_wflndscp_wide_sf) = "geometry"

# treatment targets
googlesheets4::gs4_auth(email = "geo.woolsey@gmail.com")
treatment_targets <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1qVtOIcpJuN-7QOWY_rhnSIUGILvbOXeM_ASXxa6a5q8/edit?usp=sharing") |> 
  dplyr::inner_join(
    constrained_by_wflndscp_wide_sf |> 
      sf::st_drop_geometry() |> 
      dplyr::select(
        state,name,area_name
      )
    , by = dplyr::join_by(state,name)
  )

```


```{r include=FALSE, eval=FALSE}
mapview::mapview(constrained_byftr_huc12_wide_sf, zcol = "cnstrnt_class"
  , col.regions = RColorBrewer::brewer.pal(n=3,name="RdYlBu") |> rev()
  , alpha.regions = 0.6
  , lwd = 0.2
  , label = FALSE
  , legend = FALSE)
xxx <- sf::st_read("../data/treatment_in_landscapes.shp")

```

## Forest Management Activities (FACTS)

The Hazardous Fuel Treatments metadata file is available [here](https://data.fs.usda.gov/geodata/edw/edw_resources/meta/S_USA.Activity_HazFuelTrt_PL.xml) and the Timber Harvests metadata file is available [here](https://data.fs.usda.gov/geodata/edw/edw_resources/meta/S_USA.Activity_TimberHarvest.xml). 

[This appendix](https://www.fs.usda.gov/Internet/FSE_DOCUMENTS/fseprd539041.pdf) includes a listing of all the active and inactive FACTS activity codes, as well as detailed descriptions of some of the codes.

```{r facts-load}
# years back to keep
years_back <- 10
# check for data and download
zip_path <- c(
    "https://data.fs.usda.gov/geodata/edw/edw_resources/fc/S_USA.Activity_HazFuelTrt_PL.gdb.zip"  # haz fuel
    , "https://data.fs.usda.gov/geodata/edw/edw_resources/fc/S_USA.Activity_TimberHarvest.gdb.zip" # timber harv
  )
for (i in 1:length(zip_path)) {
  f_nm <- paste0( "../data/"
    , str_split(zip_path[i], "/", simplify = TRUE)[length(str_split(zip_path[i], "/", simplify = TRUE))]
  )
  fldr <- paste0(gsub(".zip", "", f_nm))
  options(timeout = 60 * 15)
  if(file.exists(fldr) == FALSE){
    # download data
    if(file.exists(f_nm) == FALSE){
      download.file(zip_path[i], destfile = f_nm)
    }else{print("file already exists")}
    # unzip
    unzip(f_nm, overwrite=TRUE, exdir = fldr)
    file.remove(f_nm)
  }else{print("unzip already exists")}
}
# haz_fuel
haz_fuel <- sf::st_read(
    dsn = "../data/S_USA.Activity_HazFuelTrt_PL.gdb/S_USA.Activity_HazFuelTrt_PL.gdb"
    , layer = "Activity_HazFuelTrt_PL"
    # , query = "SELECT * FROM \"Activity_HazFuelTrt_PL\" 
    #             WHERE 
    #               STAGE_VALUE IN ('ACCOMPLISHED')
    #               AND FISCAL_YEAR_COMPLETED = '2023'
    #   "
  ) |>  
  rename_with(~ tolower(
    gsub(" ", "_", 
       str_trim(gsub("\\s+", " ", .x))
    )
  )) |>
  # filter
  dplyr::filter(
    tolower(stage_value) == "accomplished"
    & tolower(cat_nm) %in% c("mechanical", "fire")
    & !stringr::str_detect("pile burn", tolower(treatment_type))
    & fiscal_year_completed >= lubridate::year(Sys.Date())-years_back+1
    & fiscal_year_completed <= lubridate::year(Sys.Date())
    # & lubridate::year(date_completed) >= lubridate::year(Sys.Date())-years_back+1
    # & lubridate::year(date_completed) <= lubridate::year(Sys.Date())
  )
  #rename sf geom column
  names(haz_fuel)[names(haz_fuel)==tolower(attr(haz_fuel, "sf_column"))] = "geometry"
  sf::st_geometry(haz_fuel) = "geometry"
  # transform
  haz_fuel <- haz_fuel |>  
    sf::st_transform(crs=transform_crs) |>  
    dplyr::filter(sf::st_is_valid(geometry)) |>  
    dplyr::mutate(
      facts_src = "haz_fuel"
      , treatment_type = trimws(treatment_type)
      , treatment_category = tolower(cat_nm)
      # , treatment_area_ha = as.numeric(sf::st_area(geometry))/10000
    ) |> 
    dplyr::select(suid, facts_src, treatment_category, treatment_type, date_completed, fiscal_year_completed)
  gc()
# timber harvest
harvests <- sf::st_read(
    dsn = "../data/S_USA.Activity_TimberHarvest.gdb/S_USA.Activity_TimberHarvest.gdb"
    , layer = "Activity_TimberHarvest"
    # , query = "SELECT * FROM \"Activity_TimberHarvest\"
    #             WHERE
    #               STAGE_DESC IN ('ACCOMPLISHED')
    #               AND FY_COMPLETED = '2023'
    #   "
  ) |> 
  rename_with(~ tolower(
    gsub(" ", "_",
       str_trim(gsub("\\s+", " ", .x))
    )
  )) |>  
  dplyr::mutate(fiscal_year_completed = as.numeric(fy_completed)) |> 
  dplyr::filter(
    tolower(stage_desc) == "accomplished"
    & tolower(treatment_type) != "n/a"
    & fiscal_year_completed >= lubridate::year(Sys.Date())-years_back+1
    & fiscal_year_completed <= lubridate::year(Sys.Date())
    # & lubridate::year(date_completed) >= lubridate::year(Sys.Date())-years_back+1
    # & lubridate::year(date_completed) <= lubridate::year(Sys.Date())
  )
  #rename sf geom column
  names(harvests)[names(harvests)==tolower(attr(harvests, "sf_column"))] = "geometry"
  sf::st_geometry(harvests) = "geometry"
  # transform
  harvests <- harvests |>  
    sf::st_transform(crs=transform_crs) |>  
    dplyr::filter(sf::st_is_valid(geometry)) |>  
    dplyr::mutate(
      facts_src = "harvests"
      , treatment_category = "mechanical"
      , treatment_type = trimws(treatment_type)
      # , treatment_area_ha = as.numeric(sf::st_area(geometry))/10000
    ) |> 
    dplyr::select(suid, facts_src, treatment_category, treatment_type, date_completed, fiscal_year_completed)
gc()
```

```{r, warning=F, message=F, echo=FALSE, include=FALSE}
remove(list = c("f_nm", "fldr", "zip_path"))
gc()
```

Combine treatment layers with landscape areas

```{r intrsct-ls-trt}
# combine with wfp areas
treatment_in_landscapes <- rbind(
  # harvests
    sf::st_intersection(
      harvests
      , constrained_by_wflndscp_wide_sf |> 
        dplyr::select(area_name)
    )
  , # haz fuel
    sf::st_intersection(
      haz_fuel
      , constrained_by_wflndscp_wide_sf |> 
        dplyr::select(area_name)
    )
) 
# aggregate by type, area !!!! because some treatment types might overlap spatially
treatment_by_type_area <- treatment_in_landscapes |> 
  sf::st_set_precision(1000000) |> 
  sf::st_make_valid(geometry) |> 
  dplyr::filter(sf::st_is_valid(geometry)) |>  
  dplyr::group_by(area_name, treatment_category) |> 
  dplyr::summarise(
    geometry = sf::st_union(geometry)
    , n_treatments = dplyr::n_distinct(suid)
    , min_fiscal_year_completed = min(fiscal_year_completed)
    , max_fiscal_year_completed = max(fiscal_year_completed)
  ) |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    treatment_area_ha = as.numeric(sf::st_area(geometry))/10000
    , pot_min_fiscal_year_completed = lubridate::year(Sys.Date())-years_back+1
    , pot_max_fiscal_year_completed = lubridate::year(Sys.Date())
  ) |> 
  # !!!! write out for upload to GEE analysis of treatments by nlcd cov type
  # sf::st_write(sf::st_collection_extract(treatment_by_type_area)
  #            , "../data/treatment_in_landscapes.shp",append=F)
  sf::st_drop_geometry()

# join with full data
treatment_by_type_area <- dplyr::cross_join(
    # unique trt types
    treatment_in_landscapes |> 
      sf::st_drop_geometry() |> 
      dplyr::count(treatment_category) |> 
      dplyr::select(-c(n))
    # unique areas
    , constrained_by_wflndscp_wide_sf |> 
      sf::st_drop_geometry() |> 
      dplyr::count(area_name) |> 
      dplyr::select(-c(n))
  ) |> 
  dplyr::left_join(
    treatment_by_type_area
    , by = dplyr::join_by(area_name, treatment_category)
  ) |> 
  dplyr::inner_join(constrained_by_wflndscp_wide_sf |> sf::st_drop_geometry(), by = dplyr::join_by(area_name)) |> 
  dplyr::mutate(
    treatment_area_ha = ifelse(is.na(treatment_area_ha), 0, treatment_area_ha)
    , treatment_area_acres = (treatment_area_ha*10000)/4046.85642
    , pct_treated_area = treatment_area_ha/feature_area_ha
  )

# aggregate by year, area !!!! because some treatment types might overlap spatially
treatment_by_area_yr <- treatment_in_landscapes |> 
  dplyr::mutate(treatment_year = lubridate::year(date_completed)) |> 
  dplyr::group_by(
      fiscal_year_completed
      , area_name
  ) |> 
  dplyr::summarise(geometry = sf::st_union(geometry)) |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    treatment_area_ha = as.numeric(sf::st_area(geometry))/10000
  ) |> 
  sf::st_drop_geometry()


# aggregate by year, trt type, area
treatment_by_type_area_yr <- treatment_in_landscapes |> 
  dplyr::mutate(treatment_year = lubridate::year(date_completed)) |> 
  dplyr::group_by(
      fiscal_year_completed
      , facts_src
      , treatment_category
      , area_name
  ) |> 
  dplyr::summarise(geometry = sf::st_union(geometry)) |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    treatment_area_ha = as.numeric(sf::st_area(geometry))/10000
  ) |> 
  sf::st_drop_geometry()

# create full set of data with all possible combinations
base_join_temp <- constrained_by_wflndscp_wide_sf |> 
  sf::st_drop_geometry() |> 
  dplyr::count(area_name) |> 
  dplyr::select(-c(n)) |> 
  # cross with treatment types
  dplyr::cross_join(
    treatment_by_type_area_yr |> 
      dplyr::count(facts_src,treatment_category) |> 
      dplyr::select(-c(n))
  ) |> 
  # cross with years
  dplyr::cross_join(data.frame(fiscal_year_completed = unique(treatment_by_type_area_yr$fiscal_year_completed)))
# JOIN WITH aggregated data  
# treatment_by_type_area_yr
  treatment_by_type_area_yr <- base_join_temp |> 
    dplyr::left_join(treatment_by_type_area_yr, by = dplyr::join_by(area_name,fiscal_year_completed,facts_src,treatment_category)) |> 
    dplyr::mutate(
      treatment_area_ha = ifelse(is.na(treatment_area_ha), 0, treatment_area_ha)
      , treatment_label = paste0(facts_src,": ",treatment_category) |> tolower()
      , treatment_area_acres = (treatment_area_ha*10000)/4046.85642
    ) |> 
    dplyr::inner_join(constrained_by_wflndscp_wide_sf |> sf::st_drop_geometry(), by = dplyr::join_by(area_name))

# treatment_by_area_yr
  treatment_by_area_yr <- base_join_temp |> 
    dplyr::count(area_name, fiscal_year_completed) |> 
    dplyr::select(-c(n)) |> 
    dplyr::left_join(treatment_by_area_yr, by = dplyr::join_by(area_name,fiscal_year_completed)) |> 
    dplyr::mutate(
      treatment_area_ha = ifelse(is.na(treatment_area_ha), 0, treatment_area_ha)
      , treatment_area_acres = (treatment_area_ha*10000)/4046.85642
    ) |> 
    dplyr::inner_join(constrained_by_wflndscp_wide_sf |> sf::st_drop_geometry(), by = dplyr::join_by(area_name))

```

```{r, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
remove(list = ls()[grep("_temp",ls())])
gc()
```

Combine treatment layers with watersheds

```{r intrsct-ws-trt}
# combine with wfp areas
treatment_in_watersheds <- rbind(
  # harvests
    sf::st_intersection(
      harvests
      , constrained_byftr_huc12_wide_sf |> 
        dplyr::select(area_name, huc12, cnstrnt_class, rmn_cnstrnt_class)
    )
  , # haz fuel
    sf::st_intersection(
      haz_fuel
      , constrained_byftr_huc12_wide_sf |> 
        dplyr::select(area_name, huc12, cnstrnt_class, rmn_cnstrnt_class)
    )
) 
gc()
# aggregate by trt type, area, constraint class
treatment_by_cnstrnt_type_area <- treatment_in_watersheds |> 
  dplyr::group_by(
      treatment_category
      , area_name
      , cnstrnt_class, rmn_cnstrnt_class
  ) |> 
  dplyr::summarise(
    geometry = sf::st_union(geometry)
    , n_treatments = dplyr::n_distinct(suid)
    , min_fiscal_year_completed = min(fiscal_year_completed)
    , max_fiscal_year_completed = max(fiscal_year_completed)
  ) |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    treatment_area_ha = as.numeric(sf::st_area(geometry))/10000
    , pot_min_fiscal_year_completed = lubridate::year(Sys.Date())-years_back+1
    , pot_max_fiscal_year_completed = lubridate::year(Sys.Date())
  ) |> 
  sf::st_drop_geometry()
gc()
# join with full data
treatment_by_cnstrnt_type_area <- dplyr::cross_join(
    # unique trt types
    treatment_in_landscapes |> 
      sf::st_drop_geometry() |> 
      dplyr::count(treatment_category) |> 
      dplyr::select(-c(n))
    # unique areas
    , constrained_by_wflndscp_wide_sf |> 
      sf::st_drop_geometry() |> 
      dplyr::count(area_name) |> 
      dplyr::select(-c(n))
  ) |> 
  dplyr::cross_join(
    constrained_byftr_huc12_wide_sf |> 
      sf::st_drop_geometry() |> 
      dplyr::count(cnstrnt_class, rmn_cnstrnt_class) |> 
      dplyr::select(-c(n))
  ) |> 
  dplyr::left_join(
    treatment_by_cnstrnt_type_area
    , by = dplyr::join_by(area_name, treatment_category,cnstrnt_class, rmn_cnstrnt_class)
  ) |> 
  dplyr::left_join(
    sf::st_intersection(
        constrained_byftr_huc12_wide_sf
        , constrained_by_wflndscp_wide_sf |> 
          dplyr::select(geometry)
      ) |> 
        dplyr::mutate(feature_area_ha = as.numeric(sf::st_area(geometry))/10000) |> 
        sf::st_drop_geometry() |> 
        dplyr::group_by(area_name, cnstrnt_class, rmn_cnstrnt_class) |> 
        dplyr::summarise(feature_area_ha = sum(feature_area_ha))
    , by = dplyr::join_by(area_name, cnstrnt_class, rmn_cnstrnt_class)
  ) |> 
  dplyr::mutate(
    treatment_area_ha = ifelse(is.na(treatment_area_ha), 0, treatment_area_ha)
    , treatment_area_acres = (treatment_area_ha*10000)/4046.85642
    , pct_treated_area = treatment_area_ha/feature_area_ha
  )
```

```{r, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
remove(list = ls()[grep("_temp",ls())])
remove(harvests,haz_fuel)
gc()
```

## Treatment acres by year table

```{r trt-yr-tbl, results='asis'}
treatment_table_temp <- treatment_by_type_area_yr |> 
  dplyr::filter(fiscal_year_completed>=2022) |> 
  dplyr::mutate(nm = paste(facts_src,treatment_category,sep = "_")) |> 
  dplyr::select(area_name,fiscal_year_completed,nm,tidyselect::starts_with("treatment_area")) |> 
  tidyr::pivot_wider(
    names_from = nm
    , values_from = tidyselect::starts_with("treatment_area")
    , names_glue = "{nm}_{.value}"
    , values_fill = 0
  ) |> 
  # join with targets
  dplyr::left_join(
    treatment_targets |> 
      dplyr::select(area_name, tidyselect::starts_with("target_acres_20")) |> 
      tidyr::pivot_longer(
        cols = tidyselect::starts_with("target_acres_20")
        , names_to = "fiscal_year_completed"
        , values_to = "target_area_acres"
        , names_prefix = "target_acres_"
        , values_drop_na = F
      ) |> 
      dplyr::mutate(dplyr::across(
        c(fiscal_year_completed,target_area_acres)
        , ~ as.numeric(.x)
      ))
    , by = dplyr::join_by(area_name,fiscal_year_completed)
  ) |> 
  dplyr::inner_join(
    treatment_by_area_yr |> 
      dplyr::select(area_name, fiscal_year_completed, tidyselect::starts_with("treatment_area")) |> 
      dplyr::rename_with(
        ~ paste0("total_", .x)
        , tidyselect::starts_with("treatment_area")
      )
    , by = dplyr::join_by(area_name, fiscal_year_completed)
  ) |> 
  # mutates
  dplyr::mutate(
    pct_to_target = scales::percent(total_treatment_area_acres/target_area_acres,accuracy=0.1)
    , dplyr::across(tidyselect::contains("_area_"), ~ scales::comma(.x,accuracy = 1))
  )
# make a table
kableExtra::kable(
    treatment_table_temp |> dplyr::select(
      fiscal_year_completed
      , tidyselect::ends_with("treatment_area_acres")
      , target_area_acres
      , pct_to_target
    )
    , caption = "Treatments in 21 Wildfire Crisis Strategy Priority Landscapes<br>*only treatments on National Forest System lands shown"
    , col.names = c(
      " "
      , "Timber Harvest: mechanical"
      , "Hazardous Fuel Treatment: fire"
      , "Hazardous Fuel Treatment: mechanical"
      , "Total Treated*"
      , "Target Treated"
      , "% to Target"
    )
  ) |>  
  kableExtra::add_header_above(c(" " = 1, "Acres"=5," "=1)) |>
  kableExtra::kable_classic(full_width=T) |> 
  kableExtra::pack_rows(index = table(forcats::fct_inorder(treatment_table_temp$area_name))) |>
  kableExtra::kable_styling(font_size = 11,fixed_thead = TRUE) |> 
  kableExtra::footnote(
    general = paste0(
      "treatment by fiscal year completed"
      , " | last updated: "
      , file.info("../data/S_USA.Activity_HazFuelTrt_PL.gdb/")$ctime |> lubridate::as_date()
    )
    , symbol = c("overlapping area counted once")
  )
```

## Treatment area versus Mechanically Available Area

```{r trt-avail}
ggplot(
    data = treatment_by_type_area
    , mapping = aes(y = pct_treated_area, x = pct_rmn5_roads, fill = treatment_category)
  ) +
  geom_point(size = 4.5, alpha = 0.8,shape=21,color="gray66") + 
  ggrepel::geom_text_repel(
    mapping = 
      aes(label = stringr::str_wrap(
        ifelse(
          stringr::str_count(area_name, "\\w+")<3
          , stringr::word(area_name,1,stringr::str_count(area_name, "\\w+"))
          , stringr::word(area_name,1,3)
        )
        , 7)
      )
    , size = 2
    , color = "gray33"
    , segment.size = 0.2
    , segment.alpha = 0.6
  ) + 
  facet_grid(cols = vars(stringr::str_to_title(treatment_category))) +
  scale_fill_manual(values = c("firebrick","navy")) +
  scale_x_continuous(labels = scales::percent_format(), breaks = scales::extended_breaks(n=8)) +
  scale_y_continuous(labels = scales::percent_format(), breaks = scales::extended_breaks(n=8)) +
  labs(
    fill = ""
    , y = "% Landscape Area Treated"
    , x = "% Forested Area\nMechanically Available"
    , title = paste0(
      "Treatments Completed FY-"
      , min(treatment_by_type_area$pot_min_fiscal_year_completed)
      , " to FY-"
      , max(treatment_by_type_area$pot_max_fiscal_year_completed)
    )
    , subtitle = "*only treatments on National Forest System lands included"
  ) +
  theme_light() +
  theme(
    legend.position = "none" # c(0.9, 0.9)
    , axis.title = element_text(size=9)
    , axis.text.x = element_text(size=7)
    , strip.text = element_text(color = "black", face = "bold")
    , plot.title = element_text(size = 9)
    , plot.subtitle =  element_text(size = 8)
  )

```

## Treatment in Subwatersheds by Level of Constraint

```{r trt-sw, fig.height=9}
ggplot(
  data = treatment_by_cnstrnt_type_area |> dplyr::filter(treatment_category=="mechanical")
  , mapping = aes(y = cnstrnt_class, x = pct_treated_area, fill = cnstrnt_class)
) +
  geom_col(width = 0.7) +
  geom_text(
    mapping = aes(
      label = scales::percent(pct_treated_area, accuracy = 0.1)
    )
    , color = "black", size = 3
    , hjust = -0.1
  ) +
  scale_fill_brewer(type = "div", palette = "RdYlBu", direction = -1) +
  facet_wrap(
    facets = vars(area_name)
    , ncol = 3
    , labeller = label_wrap_gen(width = 35, multi_line = TRUE)
  ) +
  scale_x_continuous(expand = expansion(mult = c(0, .1)),labels = scales::percent_format()) +
  labs(
    y = "Level of\nConstraint"
    , x = "% Subwatershed Area\nMechanically Treated"
    , title = paste0(
      "Mechanical Treatments Completed FY-"
      , min(treatment_by_type_area$pot_min_fiscal_year_completed)
      , " to FY-"
      , max(treatment_by_type_area$pot_max_fiscal_year_completed)
    )
    , subtitle = "*only treatments on National Forest System lands included"
  ) +
  theme_light() +
  theme(
    legend.position = "none"
    , axis.title = element_text(size=9)
    , axis.text.x = element_text(size=7)
    , plot.title = element_text(size = 9)
    , plot.subtitle =  element_text(size = 8)
  )
```

## Total Area Treated by Level of Constraint

```{r trt-sw-tot}
treatment_by_cnstrnt_type_area |> 
  dplyr::group_by(treatment_category, cnstrnt_class) |> 
  dplyr::summarise(
    dplyr::across(
      tidyselect::starts_with("treatment_area_")
      , ~ sum(.x,na.rm = T)
    )
  ) |> 
ggplot(
  mapping = aes(y = cnstrnt_class, x = treatment_area_acres, fill = cnstrnt_class)
) +
  geom_col(width = 0.7) +
  geom_text(
    mapping = aes(
      label = scales::comma(treatment_area_ha,suffix = "k ha", scale = 1e-3, accuracy = 0.1) 
    )
    , color = "black", size = 3
    , hjust = -0.1
  ) +
  geom_text(
    mapping = aes(
      label = scales::comma(treatment_area_acres,suffix = "k ac", scale = 1e-3, accuracy = 0.1) 
    )
    , color = "black", size = 2.5
    , hjust = -0.15
    , vjust = 3
  ) +
  scale_fill_brewer(type = "div", palette = "RdYlBu", direction = -1) +
  facet_grid(cols = vars(stringr::str_to_title( treatment_category)))+
  scale_x_continuous(expand = expansion(mult = c(0, .2)),labels = scales::comma_format()) +
  labs(
    y = "Level of\nConstraint"
    , x = "Area Treated"
    , title = paste0(
      "Treatments Completed FY-"
      , min(treatment_by_type_area$pot_min_fiscal_year_completed)
      , " to FY-"
      , max(treatment_by_type_area$pot_max_fiscal_year_completed)
    )
    , subtitle = "*only treatments on National Forest System lands included"
  ) +
  theme_light() +
  theme(
    legend.position = "none"
    , axis.title = element_text(size=9)
    , axis.text.x = element_blank()
    , axis.ticks.x = element_blank()
    , strip.text = element_text(color = "black", face = "bold")
    , plot.title = element_text(size = 9)
    , plot.subtitle =  element_text(size = 8)
  )
```

## Treatment by Cover Type

What is the forest versus shrubland classification of the area treated? This [GEE script](https://code.earthengine.google.com/15afaf7d703102e82f82d482552b2356?noload=true) was used to calculate the area within treatment boundaries by NLCD landcover class.

```{r trt-nlcd}
# read data
treatment_in_landscapes_statistics <- readr::read_csv("../data/treatment_in_landscapes_statistics.csv") |> 
  dplyr::rename_with(
    ~ gsub("^\\_|\\_$", "", .x)
    , everything()
  ) |> 
  dplyr::select(area_nm,tidyselect::ends_with("_m2"),tidyselect::ends_with("_fs_"),trtmnt) |> 
  dplyr::rename(area_name = area_nm,treatment_category=trtmnt
                ,pot_min_fiscal_year_completed=mn_fs_
                ,pot_max_fiscal_year_completed=mx_fs_
  ) |> 
  dplyr::mutate(dplyr::across(
      tidyselect::ends_with("_m2")
      , ~ .x/10000
    )
  ) |> 
  dplyr::rename_with(
    ~ gsub("_m2", "_ha", .x)
    , tidyselect::ends_with("_m2")
  ) |> 
  dplyr::group_by(area_name,treatment_category
                  ,pot_min_fiscal_year_completed,pot_max_fiscal_year_completed
  ) |> 
  dplyr::summarise(
    dplyr::across(
      tidyselect::ends_with("_ha")
      , ~ sum(.x,na.rm = T)
    )
  ) |> 
  dplyr::ungroup()
# get color list
nlcd_color_temp <- FedData::nlcd_colors() |> dplyr::filter(ID %in% c(42,52)) |> dplyr::pull(Color)
# plot
treatment_in_landscapes_statistics |> 
  dplyr::mutate(
    dplyr::across(
      c(forest_area_ha,shrubland_area_ha)
      , ~ .x/feature_area_ha
      , .names = "pct_{.col}"
    )
  ) |>
  dplyr::mutate(
    pct_other_area_ha = 1-(pct_forest_area_ha+pct_shrubland_area_ha)
  ) |> 
  tidyr::pivot_longer(
      cols = tidyselect::starts_with("pct_")
      , names_to = "class"
      , values_to = "pct_treatment_area"
      , names_prefix = "pct_"
      , values_drop_na = F
    ) |>
  dplyr::mutate(
    class = stringr::str_remove_all(class,"_area_ha") |> stringr::str_to_title()
    , treatment_category = stringr::str_to_title(treatment_category)
  ) |> 
ggplot(
    mapping = aes(x = pct_treatment_area, y = reorder(area_name,desc(area_name)), fill=class)
  ) +
  geom_col(width = 0.7, alpha=0.8) +
  geom_text(
    mapping = aes(
      label = scales::percent(ifelse(pct_treatment_area>.05,pct_treatment_area,NA), accuracy = 1)
    )
    , position = position_stack(vjust = 0.5)
    , color = "black", size = 3
  ) +
  facet_grid(cols = vars( treatment_category))+
  scale_fill_manual(values = c("Forest"=nlcd_color_temp[1],"Shrubland"=nlcd_color_temp[2],"Other"="gray88")) +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(
    fill = "NLCD\nCover\nType"
    , y = ""
    , x = "% Area Treated"
    , title = paste0(
      "Treatments Completed FY-"
      , min(treatment_in_landscapes_statistics$pot_min_fiscal_year_completed)
      , " to FY-"
      , max(treatment_in_landscapes_statistics$pot_max_fiscal_year_completed)
    )
    , subtitle = "*only treatments on National Forest System lands included"
  ) +
  theme_light() +
  theme(
    legend.position = "top" # c(0.9, 0.9)
    , legend.title = element_text(size=9)
    , axis.title = element_text(size=9)
    , axis.text.x = element_text(size=7)
    , strip.text = element_text(color = "black", face = "bold")
    , plot.title = element_text(size = 9)
    , plot.subtitle =  element_text(size = 8)
  )
```

