# Scenario Analysis: WCS Priority Landscapes

```{r, include=FALSE, warning=F, message=F}
# knit options
knitr::opts_chunk$set(
  echo = TRUE
  , warning = FALSE
  , message = FALSE
  , results='hide'
  , fig.width = 10
  , fig.height = 7
)
# bread-and-butter
library(tidyverse)
library(lubridate)
library(viridis)
library(scales)
library(latex2exp)
# visualization
library(kableExtra)
library(cowplot)
library(RColorBrewer)
library(mapview) #Interactive maps
library(leafpop) #map html popup
# spatial analysis
library(sf)
library(USAboundaries)
# set seed
set.seed(11)
```

```{r, results='hide'}
# turn off the s2 processing 
## https://stackoverflow.com/questions/68478179/how-to-resolve-spherical-geometry-failures-when-joining-spatial-data
sf::sf_use_s2(FALSE)
```

See [this prior section](#wcs_intro) for initial [Wildfire Crisis Strategy]((https://www.fs.usda.gov/managing-land/wildfire-crisis)) (WCS) analysis and background information.

```{r, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
remove(list = ls())
gc()
```

## Scenarios Considered

There are three scenarios considered in this analysis of the constraints to mechanical forest health and fuel reduction treatments:

```{r sc-tab, results='asis'}
# mechanical mgmt allowed if:
n_sc_temp <- 3
data.frame(
  scenario = 1:3
  , cover = rep("Forest or Shrubland",n_sc_temp)
  , protected = rep("Not Protected",n_sc_temp)
  , slope = c("<35%","<50%","<50%")
  , admin = c("No Designation","No Designation","Any Designation")
  , riparian = c(">100ft",">100ft",">50ft")
  , road = c("<1,000ft","<2,000ft","<2,000ft")
) |> 
  tidyr::pivot_longer(
    cols = -c(scenario)
  ) |> 
  tidyr::pivot_wider(
    names_from = scenario
    , values_from = value
    , names_prefix = "scenario_"
  ) |> 
  dplyr::mutate(
    name = factor(
      name
      , levels = c(
        "cover"
        , "protected"
        , "slope"
        , "admin"
        , "riparian"
        , "road"
      )
      , labels = c(
        "NLCD Cover Type"
        , "Protected or<br>IRA Status"
        , "Slope"
        , "Administrative<br>Designation"
        , "Riparian<br>Buffer"
        , "Distance to<br>Nearest Road"
      )
      , ordered = T
    )
  ) |> 
# make table
kableExtra::kable(
    caption = "Scenarios Considered for Determining Mechanical Treatment Operability<br>Mechanical treatment allowed if:"
    , col.names = c(
      ""
      , "Scenario 1<br>Most Constrained"
      , "Scenario 2<br>Moderate"
      , "Scenario 3<br>Least Constrained"
    )
    , escape = F
  ) |>  
  kable_classic(full_width=T) |> 
  kableExtra::kable_styling(font_size = 11,fixed_thead = TRUE)
```

## Data Preparation

### Load landscape-level data

Landscape-level constraint analysis data was created via this [Google Earth Engine script](https://code.earthengine.google.com/2b330779ad5c813bdd40bde765c4b079?noload=true); WCS priority landscape spatial data was created in this [prior section](#wflndscp).

```{r ls-ld-dta}
# load wcs priority landscapes
wf_landscapes <- sf::st_read("../data/constrained_by_wflndscp_wide_sf.gpkg") |> 
  dplyr::select(1:10)
  #rename sf geom column
    names(wf_landscapes)[names(wf_landscapes)==tolower(attr(wf_landscapes, "sf_column"))] = "geometry"
    sf::st_geometry(wf_landscapes) = "geometry"
# set crs
transform_crs <- sf::st_crs(wf_landscapes)
# load landscape constraint scenario data
constrained_by_scnro_ls <- list.files("../data/wildfirepriority/all/",pattern = "\\.csv$") %>%
  purrr::keep(stringr::str_starts(.,"wfpriority_all_sc")) %>% 
  purrr::map(function(x){
    readr::read_csv(
      paste0("../data/wildfirepriority/all/",x)
      , name_repair = "universal"
      , col_types = cols(.default = "c")
    ) %>% 
    dplyr::rename_with(tolower) %>% 
    dplyr::rename_with(make.names) %>% 
    dplyr::select(state,name,tidyselect::ends_with("_m2"),tidyselect::starts_with("pct_")) %>% 
    dplyr::mutate(scenario_id = stringr::word(x,3,sep="_") %>% readr::parse_number()) %>% 
    dplyr::relocate(scenario_id)
  }) %>%
  dplyr::bind_rows() %>%
  dplyr::inner_join(
    wf_landscapes %>%
      sf::st_drop_geometry() %>%
      dplyr::select(state,name,area_name)
    , by = dplyr::join_by(state,name)
  ) %>%
  dplyr::relocate(area_name,.after = "scenario_id") %>%
  dplyr::group_by(area_name,scenario_id) %>%
  dplyr::filter(dplyr::row_number()==1) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    dplyr::across(
      tidyselect::ends_with("_m2")
      , ~ as.numeric(.x) / 10000
    )
    , dplyr::across(
      tidyselect::starts_with("pct_")
      , ~ as.numeric(.x)
    )
  ) %>%
  dplyr::rename_with(
    ~ gsub("_m2", "_ha", .x)
    , tidyselect::ends_with("_m2")
  ) %>%
  # calculate pct reduction
  dplyr::mutate(
    pct_rdctn1_protected = -1*(1 - pct_rmn1_protected)
    , pct_rdctn2_slope = -1*(pct_rmn1_protected - pct_rmn2_slope)
    , pct_rdctn3_administrative = -1*(pct_rmn2_slope - pct_rmn3_administrative)
    , pct_rdctn4_riparian = -1*(pct_rmn3_administrative - pct_rmn4_riparian)
    , pct_rdctn5_roads = -1*(pct_rmn4_riparian - pct_rmn5_roads)
    , pct_rdctn_total = -1*(1 - pct_rmn5_roads)
    , pct_covertype_area = covertype_area_ha/feature_area_ha
    # scenario description
    , scenario_lab = factor(
      scenario_id
      , levels = 1:3
      , labels = paste0("Scenario ", 1:3)
      , ordered = T
    ) |> forcats::fct_rev()
    , scenario_desc = factor(
      scenario_id
      , levels = 1:3
      , labels = c("Scenario 1\n(status quo)", "Scenario 2\n(slopes+roads)", "Scenario 3\n(slopes+roads+admin)")
      , ordered = T
    )
  )
  

```

```{r, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
remove(list = ls()[grep("_temp",ls())])
gc()
```

## Load fireshed project area data

Data created via this [Google Earth Engine script](https://code.earthengine.google.com/003e3994cfc4c469d52d224225a4b109?noload=true)

See [this section](#fsheds) for exploration of fireshed and project area spatial data

```{r fs-ld-dta}
# load firesheds
fireshed <- sf::st_read("../data/firesheds/fireshed.gpkg") |> 
  sf::st_transform(transform_crs) |> 
  dplyr::mutate(
    crisis_strategy = ifelse(is.na(crisis_strategy),"No WCS Status",crisis_strategy) |> 
      as.factor() |> 
      forcats::fct_shift()
  )
  #rename sf geom column
    names(fireshed)[names(fireshed)==tolower(attr(fireshed, "sf_column"))] = "geometry"
    sf::st_geometry(fireshed) = "geometry"
# load fireshed project areas
fireshed_proj_area <- sf::st_read("../data/firesheds/fireshed_proj_area.gpkg") |> 
  sf::st_transform(transform_crs) |> 
  dplyr::mutate(
    fireshed_crisis_strategy = ifelse(is.na(fireshed_crisis_strategy),"No WCS Status",fireshed_crisis_strategy) |> 
      as.factor() |> 
      forcats::fct_shift()
  )
  #rename sf geom column
    names(fireshed_proj_area)[names(fireshed_proj_area)==tolower(attr(fireshed_proj_area, "sf_column"))] = "geometry"
    sf::st_geometry(fireshed_proj_area) = "geometry"
# load fireshed constraint scenario data
constrained_by_scnro_ls_pa <-
  list.files("../data/wildfirepriority/fireshed/",pattern = "\\.csv$") %>%
  purrr::keep(stringr::str_starts(.,"wfpriority_fireshed_sc")) %>% 
  purrr::map(function(x){
    readr::read_csv(
      paste0("../data/wildfirepriority/fireshed/",x)
      , name_repair = "universal"
      , col_types = cols(.default = "c")
    ) %>% 
    dplyr::rename_with(tolower) %>% 
    dplyr::rename_with(make.names) %>% 
    dplyr::select(state,name,pa_id,tidyselect::ends_with("_m2"),tidyselect::starts_with("pct_")) %>% 
    dplyr::mutate(scenario_id = stringr::word(x,3,sep="_") %>% readr::parse_number()) %>% 
    dplyr::relocate(scenario_id)
  }) %>%
  dplyr::bind_rows() %>%
  dplyr::inner_join(
    wf_landscapes %>%
      sf::st_drop_geometry() %>%
      dplyr::select(state,name,area_name)
    , by = dplyr::join_by(state,name)
  ) %>%
  dplyr::relocate(area_name,.after = "scenario_id") %>%
  dplyr::mutate(
    dplyr::across(
      tidyselect::ends_with("_m2")
      , ~ as.numeric(.x) / 10000
    )
    , dplyr::across(
      tidyselect::starts_with("pct_")
      , ~ as.numeric(.x)
    )
  ) %>%
  dplyr::rename_with(
    ~ gsub("_m2", "_ha", .x)
    , tidyselect::ends_with("_m2")
  ) %>%
  dplyr::group_by(area_name,pa_id,scenario_id) %>%
  dplyr::arrange(desc(pct_pa_intrsct)) %>%
  dplyr::filter(dplyr::row_number()==1) %>%
  dplyr::ungroup() %>%
  dplyr::filter(pct_pa_intrsct>=0.25) %>%
  # calculate pct reduction
  dplyr::mutate(
    pct_rdctn1_protected = -1*(1 - pct_rmn1_protected)
    , pct_rdctn2_slope = -1*(pct_rmn1_protected - pct_rmn2_slope)
    , pct_rdctn3_administrative = -1*(pct_rmn2_slope - pct_rmn3_administrative)
    , pct_rdctn4_riparian = -1*(pct_rmn3_administrative - pct_rmn4_riparian)
    , pct_rdctn5_roads = -1*(pct_rmn4_riparian - pct_rmn5_roads)
    , pct_rdctn_total = -1*(1 - pct_rmn5_roads)
    , pct_covertype_area = covertype_area_ha/feature_area_ha
    # calculate level of constraint
      , cnstrnt_lvl = dplyr::case_when(
          -pct_rdctn_total >= 0.85 ~ 1
          , -pct_rdctn_total >= 0.65 ~ 2
          , -pct_rdctn_total >= 0.0 ~ 3
        )
      , cnstrnt_class = factor(
          cnstrnt_lvl 
          , levels = 1:3
          , labels = c("high constraint", "med. constraint", "low constraint")
          , ordered = T
        ) %>% forcats::fct_rev()
      , rmn_cnstrnt_class = factor(
          cnstrnt_lvl 
          , levels = 1:3
          , labels = c("0–15% treatable", "16–35% treatable", ">35% treatable")
          , ordered = T
        ) %>% forcats::fct_rev()
      # scenario description
      , scenario_lab = factor(
          scenario_id
          , levels = 1:3
          , labels = paste0("Scenario ", 1:3)
          , ordered = T
        ) |> forcats::fct_rev()
      , scenario_desc = factor(
        scenario_id
        , levels = 1:3
        , labels = c("Scenario 1\n(status quo)", "Scenario 2\n(slopes+roads)", "Scenario 3\n(slopes+roads+admin)")
        , ordered = T
      )
  ) %>% 
  # join with fireshed data
  dplyr::inner_join(
    fireshed_proj_area %>%
      sf::st_drop_geometry() %>%
      dplyr::select(pa_id, tidyselect::starts_with("pa_exposure"), tidyselect::starts_with("fireshed_")) %>%
      dplyr::mutate(pa_id=as.character(pa_id))
    , by = dplyr::join_by(pa_id)
  )
```

```{r, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
remove(list = ls()[grep("_temp",ls())])
gc()
```

## Landscape-level analysis 

### Reduction Treatable Area Table

```{r ls-tab1, results='asis'}
scnum_temp<-2
  tbl_temp <- constrained_by_scnro_ls |> 
    dplyr::filter(scenario_id==scnum_temp) |> 
    dplyr::mutate(
      dplyr::across(
        tidyselect::ends_with("_ha")
        , ~ scales::comma(.x, accuracy = 1)
      )
      , dplyr::across(
        tidyselect::starts_with("pct_")
        , ~ scales::percent(.x, accuracy = 0.1)
      )
    ) |> 
    dplyr::select(
      state
      , name
      , covertype_area_ha
      , pct_covertype_area
      , pct_rdctn1_protected
      , pct_rdctn2_slope
      , pct_rdctn3_administrative
      , pct_rdctn4_riparian
      , pct_rdctn5_roads
      , rmn5_roads_area_ha
      , pct_rmn5_roads
    ) |> 
    dplyr::arrange(state,name)
  # make table 
  kableExtra::kable(
      tbl_temp |> dplyr::select(-c(state))
      , caption = paste0("<b><font color=navy>Scenario ",scnum_temp,"</font></b><br>percent reduction of different types of constraints on mechanical treatment")
      , col.names = c(
        ""
        , "Forest+Shrub\n(ha)", "Forest+Shrub\n%"
        , "Protected"
        , "Slope\nSteepness"
        , "Administrative"
        , "Riparian\nBuffer"
        , "Road\nDistance"
        , "Remaining (ha)"
        , "Remaining (%)"
      )
      , escape = F
    ) |>  
    add_header_above(c(" " = 1, "Area of\nPriority Landscape"=2, "Constraint\nLeast Flexible to Most Flexible" = 5, " " = 2)) |>
    kable_classic(full_width=T) |> 
    pack_rows(index = table(forcats::fct_inorder(tbl_temp$state))) |> 
    kableExtra::kable_styling(font_size = 11,fixed_thead = TRUE) |>  
    kableExtra::scroll_box(width = "740px")
  
```

```{r, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
remove(list = ls()[grep("_temp",ls())])
gc()

```

### Change in Available by Scenario

```{r ls-chg-avai, fig.height=9}
ggplot(
    data = constrained_by_scnro_ls
    , mapping = aes(x=scenario_desc,y=pct_rmn5_roads,group=area_name)
    ) +
    geom_line(mapping=aes(color = area_name), linewidth = 1.5) +
    geom_label(
      mapping=aes(label = scales::percent(pct_rmn5_roads, scale = 100, accuracy = 1))
      , color = "black"
      , size = 3
      , label.padding = unit(0.15, "lines")
    ) +
    facet_wrap(facets = vars(area_name)
      , ncol = 3
      , labeller = label_wrap_gen(width = 35, multi_line = TRUE)
    ) +
    scale_color_viridis_d(option = "turbo", alpha = 0.8) +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.1)), labels = scales::percent_format(), breaks = scales::extended_breaks(6)) +
    # scale_x_discrete(labels = scales::label_wrap(20)) +
    labs(
      x = "Most Restrictive \U2192 Least Restrictive"
      , y = "Percent Treatable Area Remaining"
    ) +
    theme_light() +
    theme(
      legend.position = "none"
      , axis.text.y = element_text(size=7)
      , axis.text.x = element_text(size=7.5)
    )
```

### Reduction by Constraint

```{r ls-rdctn, fig.height=9}
# reshape
constrained_by_scnro_ls_long <- constrained_by_scnro_ls |>
  dplyr::select(state, name, area_name, tidyselect::starts_with("scenario_"), tidyselect::starts_with("pct_rdctn")) |> 
  tidyr::pivot_longer(
    cols = tidyselect::starts_with("pct_rdctn")
    , names_to = "constraint"
    , values_to = "pct_rdctn"
    , names_prefix = "pct_rdctn"
    , values_drop_na = F
  ) |> 
  tidyr::separate_wider_delim(constraint, "_", names = c("constraint_lvl", "constraint")) |> 
  dplyr::mutate(
    constraint_lvl = as.numeric(constraint_lvl)
    , constraint = factor(
        constraint
        , ordered = TRUE
        , levels = c(
          "protected"
          , "slope"
          , "administrative"
          , "riparian"
          , "roads"
          , "total"   
        )
        , labels = c(
          "Protected"
          , "Slope\nSteepness"
          , "Administrative"
          , "Riparian\nBuffer"
          , "Road\nDistance"
          , "Total"
        )
      ) |> forcats::fct_rev()
  ) |> 
  dplyr::left_join(
    constrained_by_scnro_ls |> dplyr::select(state,name,scenario_id,pct_rdctn_total)
    , by = join_by(state,name,scenario_id)
  )
# plot
ggplot() +
  geom_col(
    data = constrained_by_scnro_ls_long |> dplyr::filter(constraint!="Total")
    , mapping = aes(y = scenario_lab, x = pct_rdctn, fill = constraint)
    , color = NA, width = 0.7
  ) +
  geom_text(
    data = constrained_by_scnro_ls_long |> dplyr::filter(constraint!="Total")
    , mapping = aes(
      y = scenario_lab, x = pct_rdctn
      , label = scales::percent(ifelse(pct_rdctn<.06*-1,pct_rdctn,NA), accuracy = 1)
      , fontface = "bold"
    )
    , position = position_stack(vjust = 0.5)
    , color = "black", size = 3
  ) +
  geom_text(
    data = constrained_by_scnro_ls_long |> dplyr::filter(constraint=="Total")
    , mapping = aes(
      y = scenario_lab, x = pct_rdctn_total
      , label = scales::percent(pct_rdctn_total, accuracy = 1)
    )
    , color = "black", size = 3.5
    , hjust = -0.1
  ) +
  facet_wrap(facets = vars(area_name)
      , ncol = 3
      , labeller = label_wrap_gen(width = 35, multi_line = TRUE)
    ) +
  scale_fill_viridis_d(option = "plasma", alpha = 0.7) +
  scale_x_reverse(expand = expansion(mult = c(0, .12)),labels = scales::percent_format()) +
  labs(
    fill = ""
    , y = ""
    , x = "Constraint Reduction in Treatable Area (%)"
  ) +
  theme_light() +
  theme(
    legend.position = "top"
    , legend.direction  = "horizontal"
    , legend.title = element_text(size=7)
    , axis.title = element_text(size=9)
    , axis.text.x = element_blank()
    
  )
```

## Fireshed-level analysis  

Based on model simulations of how much area generally needs to be treated to influence wildfire behavior, we binned the firesheds into three classes of mechanical constraint: 

* **high** (85–100% [i.e., only 0–15% is available for mechanical treatment]): fuels treatment would principally need to rely on fire
* **medium** (65– 84%): could use a combination of fire and mechanical thinning
* **low** (65%): could effectively influence wildfire behavior with mechanical treatment alone

### Distribution of Fireshed Constraint

```{r fs-cnstrnt-dist, fig.height=8}
constrained_by_scnro_ls_pa |> 
  dplyr::count(area_name,scenario_desc,cnstrnt_class) |> 
  dplyr::group_by(area_name,scenario_desc) |> 
  dplyr::mutate(
    pct = n/sum(n)
    , high_pct=max(ifelse(cnstrnt_class=="high constraint",pct,0)) 
    , tot = sum(n)
  ) |> 
ggplot() +
  geom_col(
    mapping = aes(x = pct, y = reorder(area_name, high_pct), fill=cnstrnt_class)
    ,width = 0.7, alpha=0.8
  ) +
  geom_text(
    mapping = aes(x = pct, y = reorder(area_name, high_pct), group=cnstrnt_class
        ,label = scales::percent(ifelse(pct>=0.05,pct,NA), accuracy = 1)
      )
    , position = position_stack(vjust = 0.5)
    , color = "black", size = 3
  ) +
  # geom_text(
  #     data = constrained_byftr_huc12_wide |>
  #       dplyr::group_by(area_name) |>
  #       dplyr::summarise(n=n(), high_n=sum(ifelse(cnstrnt_class=="high constraint",1,0)))
  #     , mapping = aes(x = -0.05,y=reorder(area_name, -(high_n/n)),label=paste0("n=",scales::comma(n)))
  #     , size = 3
  #     , color = "black"
  #     , hjust = 0.7
  #   ) +
  scale_fill_brewer(type = "div", palette = "RdYlBu", direction = -1) +
  facet_grid(cols = vars(scenario_desc)) +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(
    fill = "Level of\nConstraint"
    , y = ""
    , x = "% of Fireshed\nProject Areas"
  ) +
  theme_light() +
  theme(
    legend.position = "top"
    , legend.title = element_text(size=7)
    , axis.title = element_text(size=9)
    , axis.text.x = element_text(size=7)
    , strip.text = element_text(color = "black", face = "bold")
  )
```

### Distribution of Fireshed Area

```{r fs-area, fig.height=9}
# plot
ggplot(data = constrained_by_scnro_ls_pa |> dplyr::filter(scenario_id==1)
         , mapping = aes(x = feature_area_ha, y = reorder(area_name,desc(area_name) ))
    ) +
    geom_vline(
      xintercept = 
        constrained_by_scnro_ls_pa |> 
          dplyr::filter(scenario_id==1) |> 
          dplyr::pull(feature_area_ha) |> 
          median()
      , linetype="dashed", color="gray66"
    ) +
    geom_violin(aes(fill = state)) + 
    geom_boxplot(width = 0.15) +
    # geom_point(size = 0.7, color = "gray33", alpha = 0.2) +
    geom_text(
      data = constrained_by_scnro_ls_pa |> 
        dplyr::filter(scenario_id==1) |> 
        dplyr::group_by(area_name) |> 
        dplyr::summarise(n=n(), max_area=max(feature_area_ha))
      , mapping = aes(
          x = (
            constrained_by_scnro_ls_pa |> 
            dplyr::filter(scenario_id==1) |> 
            dplyr::pull(feature_area_ha) |> 
            min()
          )*.9
          ,y=reorder(area_name,desc(area_name) )
          ,label=paste0("n=",scales::comma(n))
        )
      , size = 3
      , color = "black"
      , hjust = 0.7
    ) +
    scale_fill_viridis_d(option = "viridis", alpha = 0.8) +
    scale_x_continuous(labels = scales::comma, breaks = scales::extended_breaks(n=7)) +
    labs(
      fill = ""
      , y = ""
      , x = "Fireshed Area (ha)"
    ) +
    theme_light() +
    theme(
      legend.position = "none" # c(0.9, 0.9)
      , axis.title = element_text(size=9)
      , axis.text.x = element_text(size=7)
    )
```

### Map of Firesheds by Level of Constraint

```{r fs-map-prep, results='hide'}
# polish for mapping
map_fs_temp <- fireshed_proj_area |> 
  dplyr::select(pa_id, geometry) |> 
  dplyr::mutate(pa_id=as.character(pa_id)) |> 
  dplyr::inner_join(
    constrained_by_scnro_ls_pa
    , by = dplyr::join_by("pa_id")
    , multiple = "all"
  ) |> 
  dplyr::mutate(
    dplyr::across(
      tidyselect::starts_with("pct_")
      , ~ scales::percent(as.numeric(.x), accuracy = 0.1)
    )
    , dplyr::across(
      tidyselect::ends_with("_ha")
      , ~ scales::comma(as.numeric(.x), accuracy = 1)
    )
  ) |> 
  dplyr::mutate(
    Priority.Area.Name = area_name
    , Level.of.Constraint = cnstrnt_class
    , Pct.Treatable.Class = rmn_cnstrnt_class
    , Fireshed.ProjArea.ID = pa_id
    , Fireshed.ProjArea.Area.Hectares = feature_area_ha
    , Fireshed.WCS.Status = ifelse(is.na(fireshed_crisis_strategy),"No WCS Status",fireshed_crisis_strategy)
    , ForestShrub.Area.Hectares = covertype_area_ha
    , Pct.Rdctn.Protected = pct_rdctn1_protected
    , Pct.Rdctn.Slope = pct_rdctn2_slope
    , Pct.Rdctn.Administrative = pct_rdctn3_administrative
    , Pct.Rdctn.Riparian = pct_rdctn4_riparian
    , Pct.Rdctn.Roads = pct_rdctn5_roads
    , Treatable.Area.Hectares = rmn5_roads_area_ha
    , Pct.Treatable.Area = pct_rmn5_roads
  )
# filter for mapview
mapview_fs_temp <- map_fs_temp |> 
  dplyr::filter(
    scenario_id == 2
  )
# ## filter for high priority only
# hi_map_fs_temp <- map_fs_temp |> 
#   dplyr::filter(!is.na(fireshed_crisis_strategy))
```

```{r mapview-fs, results='asis'}
# mapview
mapview::mapviewOptions(homebutton = FALSE, basemaps = c("OpenStreetMap","Esri.WorldImagery"))
mapview::mapview(wf_landscapes
        , color = "black"
        , lwd = 1
        , alpha.regions = 0
        , label = FALSE
        , legend = FALSE
        , popup = FALSE
        , layer.name = "WCS Landscapes"
        , hide = TRUE
  ) +
mapview::mapview(
  mapview_fs_temp
  , zcol = "cnstrnt_class"
  , col.regions = RColorBrewer::brewer.pal(n=3,name="RdYlBu") |> rev()
  , alpha.regions = 0.6
  , lwd = 0.2
  , label = FALSE
  , legend = FALSE
  , layer.name = "Fireshed Constraints"
  , popup = leafpop::popupTable(
      mapview_fs_temp
      , zcol = c(
        "Priority.Area.Name"
        , "Level.of.Constraint"
        , "Pct.Treatable.Class"
        , "Fireshed.ProjArea.ID"
        , "Fireshed.ProjArea.Area.Hectares"
        , "Fireshed.WCS.Status"
        , "ForestShrub.Area.Hectares"
        , "Pct.Rdctn.Protected"
        , "Pct.Rdctn.Slope"
        , "Pct.Rdctn.Administrative"
        , "Pct.Rdctn.Riparian"
        , "Pct.Rdctn.Roads"
        , "Treatable.Area.Hectares"
        , "Pct.Treatable.Area"
      )
      , row.numbers = FALSE
      , feature.id = FALSE
    )
)

```

**Scenario 2 used for map above**

### Map of High Priority Fireshed Project Areas

```{r map-hi-pri, fig.height=8, warning=F,results='hide'}
plt_fn_temp <- function(scnum=1) {
  ggplot() + 
    geom_sf(data = map_fs_temp |> dplyr::filter(scenario_id==scnum & !is.na(fireshed_crisis_strategy))
            , aes(fill = cnstrnt_class), lwd = 0.05) +
    geom_sf(
      data = USAboundaries::us_states(states = c(
          # usfs region 1-6 states
          "MT","WY","CO","NM","AZ","UT","ID","WA","OR","CA","NV"
          # , "KS","NE","SD","ND"
        )) |> 
        sf::st_transform(sf::st_crs(map_fs_temp))
      , fill = NA
      , color = "gray55"
    ) +
    geom_sf(data = wf_landscapes, fill = NA, color = "gray22", lwd = 0.2) +
    ggrepel::geom_text_repel(data = wf_landscapes
      , aes(label = stringr::str_wrap(
          dplyr::case_when(
            stringr::str_count(name, "\\w+")<2
              ~ stringr::word(name,1,stringr::str_count(name, "\\w+"))
            , stringr::str_starts(name,"Sierra and Elko") ~ stringr::word(name,1,3)
            , TRUE ~ stringr::word(name,1,2)
          )
          , 7)
          , geometry = geometry
        )
      , stat = "sf_coordinates"
      , size = 2
      , seed = 11
      # , min.segment.length = 0
    ) +
    scale_fill_brewer(type = "div", palette = "RdYlBu", direction = -1) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    labs(
      fill = ""
      , x = ""
      , y =""
      , subtitle = map_fs_temp |> dplyr::filter(scenario_id==scnum) |> 
        dplyr::pull(scenario_desc) |> unique()
    ) +
    theme_light() +
    theme(
      legend.position = c(0.9,0.9) # "top"
      , legend.text = element_text(size = 7)
      , axis.text = element_text(size=7)
    )
}
# plot
map_fs_temp |> dplyr::pull(scenario_id) |> unique() |> 
 purrr::map(plt_fn_temp)
```

**Only fireshed project areas with a high priority WCS Status shown above.**  Some fireshed project areas are within the bounds of the priority landscapes but are not within a "high priority" fireshed.

```{r, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
remove(list = ls()[grep("_temp",ls())])
gc()
```

## High-priority project areas

Models suggest that fuels reduction treatments can effectively reduce fire size and severity when 20-40% of the landscape has been treated (e.g., Finney, 2007) and the plan (USFS, 2022a) aims to treat this amount of high-risk fireshed area within the 21 priority landscapes. The total area of the 21 priority landscapes is approximately 47 million acres (19 million ha), of which 23.7 million acres (9.6 million ha) are in high-risk firesheds; an objective of treating 20-40% would indicate the need to treat between 4.7 to 9.5 million acres (1.9 to 3.8 million ha).

### Project Areas by WCS Status

```{r n-pas-wcs}
# aggregate data by area, status
wcs_status_temp <- constrained_by_scnro_ls_pa |> 
  dplyr::filter(scenario_id==1) |>
  dplyr::group_by(area_name,fireshed_crisis_strategy) |> 
  dplyr::summarise(
    n = n()
    , feature_area_ha = sum(feature_area_ha)
  ) |> 
  dplyr::group_by(area_name) |> 
  dplyr::mutate(
    tot_n = sum(n)
    , tot_area = sum(feature_area_ha)
    , pct_n = n/tot_n
    , pct_area = feature_area_ha/tot_area
  ) |> 
  dplyr::ungroup()
# plot
ggplot(data = wcs_status_temp) +
  geom_col(
    mapping = aes(y = reorder(area_name,tot_n), x = n, fill = fireshed_crisis_strategy)
    , color = NA, width = 0.7
  ) +
  geom_text(
    mapping = aes(
      y = area_name, x = n, group = fireshed_crisis_strategy
      , label = scales::comma(ifelse(n>20,n,NA), accuracy = 1)
      , fontface = "bold"
    )
    , position = position_stack(vjust = 0.5)
    , color = "black", size = 3
  ) +
  geom_text(
    data = constrained_by_scnro_ls_pa |> 
        dplyr::filter(scenario_id==1) |>
        dplyr::group_by(area_name) |> 
        dplyr::summarise(
          n = n()
          , feature_area_ha = sum(feature_area_ha)
        )
    , mapping = aes(
      y = reorder(area_name,n), x = n
      , label = scales::comma(n, accuracy = 1)
    )
    , color = "black", size = 3.5
    , hjust = -0.1
  ) +
  scale_fill_manual(values = c("All-Lands"="firebrick","USFS-Only"="orange3","No WCS Status"="gray")) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1)),labels = scales::comma_format()) +
  labs(
    fill = "High-Risk\nStatus"
    , y = ""
    , x = "# of Fireshed\nProject Areas"
  ) +
  theme_light() +
  theme(
    legend.position = "top"
    , legend.title = element_text(size=7)
    , axis.title = element_text(size=9)
    , axis.text.x = element_text(size=7)
    , strip.text = element_text(color = "black", face = "bold")
  )
```

### Area of high-priority project areas

```{r area-pas-wcs}
# data filter
wcs_status_temp |> 
  dplyr::filter(fireshed_crisis_strategy!="No WCS Status") |> 
  dplyr::group_by(area_name) |> 
  dplyr::mutate(tot_area = sum(feature_area_ha)) |> 
# plot
ggplot() +
  geom_col(
    mapping = aes(y = reorder(area_name,tot_area), x = feature_area_ha, fill = fireshed_crisis_strategy)
    , color = NA, width = 0.7
  ) +
  geom_text(
    mapping = aes(
      y = area_name, x = feature_area_ha, group = fireshed_crisis_strategy
      , label = ifelse(
          feature_area_ha<150000
          ,NA
          ,scales::comma(feature_area_ha,suffix = "k", scale = 1e-3, accuracy = 1)
        )
      , fontface = "bold"
    )
    , position = position_stack(vjust = 0.5)
    , color = "black", size = 3
  ) +
  geom_text(
    data = constrained_by_scnro_ls_pa |> 
        dplyr::filter(
          scenario_id==1
          & fireshed_crisis_strategy!="No WCS Status"
        ) |>
        dplyr::group_by(area_name) |> 
        dplyr::summarise(
          n = n()
          , feature_area_ha = sum(feature_area_ha)
        )
    , mapping = aes(
      y = reorder(area_name,feature_area_ha), x = feature_area_ha
      , label = scales::comma(feature_area_ha,suffix = "k ha", scale = 1e-3, accuracy = 1)
    )
    , color = "black", size = 3.5
    , hjust = -0.1
  ) +
  scale_fill_manual(values = c("All-Lands"="firebrick","USFS-Only"="orange3","No WCS Status"="gray")) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.15)),labels = scales::comma_format(suffix = "k ha", scale = 1e-3, accuracy = 1)) +
  labs(
    fill = "High-Risk\nStatus"
    , y = ""
    , x = "Area (ha) of Fireshed\nProject Areas"
  ) +
  theme_light() +
  theme(
    legend.position = "top"
    , legend.title = element_text(size=7)
    , axis.title = element_text(size=9)
    , axis.text.x = element_text(size=7)
    , strip.text = element_text(color = "black", face = "bold")
  )
```

```{r, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
remove(list = ls()[grep("_temp",ls())])
gc()
```

### Area Table

```{r area-tab-wcs-dta}
# area of firesheds that intersect WCS landscapes by priority status
fireshed_intersects_temp <- fireshed |>
  sf::st_join(
    wf_landscapes |>
      dplyr::select(area_name)
    , join = st_intersects
    , left = F # performs an inner join
  ) |>
  dplyr::group_by(area_name,crisis_strategy) |> 
  dplyr::summarise(
    geometry = sf::st_union(geometry)
    , fs_intersects_n = n()
  ) |> 
  dplyr::mutate(
    fs_intersects_area_ha = as.numeric(sf::st_area(geometry))/10000
  ) |> 
  sf::st_drop_geometry() |> 
  dplyr::ungroup()
# area of firesheds that intersection (crop) WCS landscapes by priority status
fireshed_crop_temp <- fireshed |>
  sf::st_intersection(
    wf_landscapes |>
      dplyr::select(area_name)
  ) |>
  dplyr::group_by(area_name,crisis_strategy) |> 
  dplyr::summarise(
    geometry = sf::st_union(geometry)
    , fs_crop_n = n()
  ) |> 
  dplyr::mutate(
    fs_crop_area_ha = as.numeric(sf::st_area(geometry))/10000
  ) |> 
  sf::st_drop_geometry() |> 
  dplyr::ungroup()
# Area of pa's that are at least 25% within WCS landscape
area_table_temp <- constrained_by_scnro_ls_pa |> 
  dplyr::filter(scenario_id==1) |> 
  dplyr::rename(crisis_strategy=fireshed_crisis_strategy) |> 
  dplyr::group_by(area_name,crisis_strategy) |> 
  dplyr::summarise(
    pa_intersects_area_ha = sum(feature_area_ha)
    , pa_intersects_covertype_area_ha = sum(covertype_area_ha)
    , pa_intersects_nlcd_area_ha = sum(nlcd_area_ha)
    , pa_crop_area_ha = sum(pa_intrsct_area_ha)
    , pa_intersects_covertype_area_ha = sum(covertype_area_ha)
    , pa_n = n()
  ) |> 
  dplyr::ungroup() |> 
  dplyr::left_join(
    fireshed_intersects_temp
    , by = dplyr::join_by(area_name,crisis_strategy)
  ) |> 
  dplyr::left_join(
    fireshed_crop_temp
    , by = dplyr::join_by(area_name,crisis_strategy)
  ) 
  # dplyr::mutate(
  #   crisis_strategy = crisis_strategy |> 
  #     stringr::str_replace_all("-"," ") |> 
  #     stringr::word(1) |> 
  #     stringr::str_replace("No","none") |> 
  #     stringr::str_to_lower()
  # ) |>
```


```{r area-tab-wcs, results='asis'}
# make table 
  kableExtra::kable(
      area_table_temp |> 
        dplyr::select(
          c(
            crisis_strategy
            , fs_intersects_n
            , fs_intersects_area_ha
            , fs_crop_area_ha
            , pa_n
            , pa_intersects_area_ha
            , pa_intersects_covertype_area_ha
            # , pa_crop_area_ha
          )
        ) |> 
        dplyr::mutate(
          dplyr::across(
            tidyselect::ends_with("_ha")
            , ~ scales::comma(.x, suffix = "k", scale = 1e-3, accuracy = 1)
          )
          , dplyr::across(
            tidyselect::ends_with("_n")
            , ~ scales::comma(.x, accuracy = 1)
          )
        )
      , caption = "<b>Wilfire Crisis Strategy Area Summary</b><br>by Strategy fireshed classification status"
      , col.names = c(
        ""
        # firesheds
        , "# Intersect\nLandscape"
        , "Area Intersect\nLandscape (ha)"
        , "Area Within\nLandscape (ha)"
        # planning areas
        , "# Intersect\nLandscape"
        , "Area Intersect\nLandscape (ha)"
        , "Forest+Shrub Intersect\nLandscape (ha)"
        # , "Area Within\nLandscape (ha)"
      )
      , escape = F
    ) |>  
    add_header_above(c(" " = 1, "Firesheds\n(~100k ha)"=3, "Planning Areas >25% in Landscape\n(~10k ha)" = 3)) |>
    kable_classic(full_width=T) |> 
    pack_rows(index = table(forcats::fct_inorder(area_table_temp$area_name))) |> 
    kableExtra::kable_styling(font_size = 11,fixed_thead = TRUE) |>  
    kableExtra::scroll_box(width = "740px")
  
```

### Objective vs. Treatable

Models suggest that fuels reduction treatments can effectively reduce fire size and severity when 20-40% of the landscape has been treated (e.g., Finney, 2007) and the Strategy (USFS, 2022a) aims to treat this amount of high-risk fireshed area within the 21 priority landscapes. The total area of the 21 priority landscapes is approximately 47 million acres (19 million ha), of which 23.7 million acres (9.6 million ha) are in high-risk firesheds; an objective of treating 20-40% would indicate the need to treat between 4.7 to 9.5 million acres (1.9 to 3.8 million ha).

*Using the area of fireshed planning areas that have at least 25% of their area within the bounds of the priority landscapes and are in a high-priority fireshed as the treatment area objective (20-40%).*

```{r obj-vs-trtbl}
# Area of pa's by level of constraint
constrained_by_scnro_ls_cnstrnt_temp <- constrained_by_scnro_ls_pa |> 
  dplyr::filter(fireshed_crisis_strategy %in% c("USFS-Only", "All-Lands")) |> 
  dplyr::group_by(scenario_id,scenario_lab,state,name,area_name,cnstrnt_class) |> 
  dplyr::summarise(
    n = n()
    , dplyr::across(
      c(feature_area_ha,covertype_area_ha,rmn5_roads_area_ha)
      , ~ sum(.x,na.rm = T)
    )
  ) |> 
  dplyr::group_by(scenario_id,scenario_lab,state,name,area_name) |> 
  dplyr::mutate(
    # cnstrnt_class = stringr::word(cnstrnt_class) |> stringr::str_remove_all("\\.")
    total_area_ha = sum(feature_area_ha)
    , total_covertype_area_ha = sum(covertype_area_ha)
    # "the need to treat 20 to 40 percent of the overall fireshed"
    , pct_treatable =  rmn5_roads_area_ha/total_area_ha
    , objective_lo_treat_area_ha = total_area_ha*.2
    , objective_hi_treat_area_ha = total_area_ha*.4
  ) |> 
  dplyr::ungroup() |> 
  dplyr::arrange(state,name,scenario_id,cnstrnt_class)
# plot
ggplot(
    data = constrained_by_scnro_ls_cnstrnt_temp |> 
        dplyr::filter(cnstrnt_class!="high constraint") |> 
        dplyr::mutate(cnstrnt_class=forcats::fct_rev(cnstrnt_class))
    , mapping = aes(
      x = pct_treatable
      , y = scenario_lab
    )
  ) +
  geom_vline(xintercept = 0.2
    , color = "gray77"
    , alpha = 0.6
  ) +
  geom_vline(xintercept = 0.4
    , color = "gray77"
    , alpha = 0.6
  ) +
  geom_rect(mapping = aes(xmin = 0.2, xmax=0.4, ymin = -Inf, ymax = Inf)
    , fill = "gray77"
    , alpha = 0.6
  ) +
  geom_col(
    mapping = aes(fill = cnstrnt_class)
    , color = NA, width = 0.7
  ) +
  geom_text(
    mapping = aes(
      group = cnstrnt_class
      , label = scales::percent(
          ifelse(pct_treatable<.06,NA,pct_treatable)
          , accuracy = 1
        )
      # , fontface = "bold"
    )
    , position = position_stack(vjust = 0.5)
    , color = "black", size = 2.5
  ) +
  # total
  geom_text(
    data = constrained_by_scnro_ls_cnstrnt_temp |> 
        dplyr::filter(cnstrnt_class!="high constraint") |> 
        dplyr::group_by(area_name, scenario_lab) |> 
        dplyr::summarise(pct_treatable=sum(pct_treatable)) |> 
        dplyr::mutate(is_gt20 = pct_treatable>=.2)
    , mapping = aes(
      y = scenario_lab, x = pct_treatable
      , label = scales::percent(pct_treatable, accuracy = 1)
      , color = is_gt20
      , fontface = "bold"
    )
    , size = 3
    , hjust = -0.1
    , show.legend = F
  ) +
  facet_grid(
    rows = vars(area_name)
    , labeller = label_wrap_gen(width = 35, multi_line = TRUE)
    , switch = "y"
  ) +
  scale_fill_manual(values = RColorBrewer::brewer.pal(n=3,name="RdYlBu")[2:3]) +
  scale_color_manual(values = c("orangered3","darkcyan")) +
  scale_x_continuous(expand = expansion(mult = c(0, .1)),labels = scales::percent_format()) +
  labs(
    fill = "Level of\nConstraint"
    , y = ""
    , x = "Percent of Total High-Risk Area"
  ) +
  theme_light() +
  theme(
    legend.position = "top"
    , legend.direction  = "horizontal"
    , legend.title = element_text(size=7)
    , axis.title = element_text(size=9)
    , axis.text.x = element_blank()
    , axis.text = element_text(size = 7)
    , panel.grid = element_blank()
    , strip.text = element_text(size = 8) # color = "black", face = "bold"
    , strip.text.y.left = element_text(angle = 0)
    , strip.placement = "outside"
  )
```


```{r, include=FALSE,eval=FALSE}
View()
  dplyr::inner_join(
    # total obj treat
    constrained_by_scnro_ls_pa |> 
      dplyr::filter(
        fireshed_crisis_strategy %in% c("USFS-Only", "All-Lands")
        
      ) |> 
      dplyr::group_by()
  )
  View()
  
  
  dplyr::group_by(state,name) |>
  dplyr::mutate(
    total_covertype_area_ha = sum(covertype_area_ha)
    , pct_treatable_tot =  rmn5_roads_area_ha/total_covertype_area_ha
  ) |> 
  dplyr::select(state,name,cnstrnt_class,rmn5_roads_area_ha,pct_treatable_tot) |>
  dplyr::filter(cnstrnt_class!="high constraint") |> 
  dplyr::mutate(cnstrnt_class=substr(cnstrnt_class,1,3)) |> 
  dplyr::rename(
        remaining_pct=pct_treatable_tot
        ,remaining_ha=rmn5_roads_area_ha
      ) |> 
      tidyr::pivot_wider(
        names_from = cnstrnt_class
        , values_from = c(tidyselect::starts_with("remaining_"))
        , names_glue = "{cnstrnt_class}_{.value}"
        , values_fill = 0
      )  |> 
  dplyr::mutate(
    tot_remaining_ha = low_remaining_ha+med_remaining_ha
    ,tot_remaining_pct = low_remaining_pct+med_remaining_pct
  ) |> 
  dplyr::relocate(tot_remaining_ha,.after = med_remaining_ha) |> 
  dplyr::mutate(
    dplyr::across(
      ends_with("_ha")
      , ~ scales::comma(.x,accuracy=1)
    )
    , dplyr::across(
      ends_with("_pct")
      , ~ scales::percent(.x,accuracy=.1)
    )
  ) |> 
  dplyr::ungroup()
  
  
  
  
  
  
  
  dplyr::rename(
    total_ha=feature_area_ha
    ,forested_ha=covertype_area_ha
    ,remaining_ha=rmn5_roads_area_ha
  ) |> 
  View()

  tidyr::pivot_wider(
    names_from = cnstrnt_class
    , values_from = c(tidyselect::ends_with("_ha"),n)
    , names_glue = "{cnstrnt_class}_{.value}"
    , values_fill = 0
  ) 
  dplyr::ungroup()
```



```{r, include=FALSE, eval=FALSE}
area_table <- constrained_wide |> 
  dplyr::left_join(
    constrained_byftr_huc12_wide |> 
      dplyr::group_by(area_name,cnstrnt_class) |> 
      dplyr::summarise(
        n = n()
        , dplyr::across(
          c(feature_area_ha,covertype_area_ha,rmn5_roads_area_ha)
          , ~ sum(.x,na.rm = T)
        )
      ) |> 
      dplyr::mutate(
        cnstrnt_class = stringr::word(cnstrnt_class) |> stringr::str_remove_all("\\.")
      ) |> 
      dplyr::rename(
        total_ha=feature_area_ha
        ,forested_ha=covertype_area_ha
        ,remaining_ha=rmn5_roads_area_ha
      ) |> 
      tidyr::pivot_wider(
        names_from = cnstrnt_class
        , values_from = c(tidyselect::ends_with("_ha"),n)
        , names_glue = "{cnstrnt_class}_{.value}"
        , values_fill = 0
      )
    , by = dplyr::join_by(area_name)
  ) |> 
  dplyr::select(area_name, tidyselect::ends_with("_ha")) |> 
  dplyr::mutate(
    dplyr::across(
      tidyselect::ends_with("_ha")
      , ~ (.x*10000)/4046.85642
      , .names = "{.col}_acres"
    )
  ) |> 
  dplyr::rename_with(
    ~ gsub("_ha_acres", "_acres", .x)
    , tidyselect::ends_with("_ha_acres")
  ) |>
  dplyr::select(
    area_name
    , feature_area_ha, feature_area_acres
    , covertype_area_ha, covertype_area_acres
    , rmn5_roads_area_ha, rmn5_roads_area_acres
    , low_total_ha, low_total_acres
    , low_forested_ha, low_forested_acres
    , low_remaining_ha, low_remaining_acres
  )
# stack acres hectares
area_table_temp <-
dplyr::bind_rows(
  area_table |> dplyr::select(area_name, tidyselect::ends_with("_ha")) |> 
    dplyr::rename_with(
      ~ gsub("_ha", "", .x)
      , tidyselect::ends_with("_ha")
    ) |> 
    dplyr::mutate(units = "ha")
  , area_table |> dplyr::select(area_name, tidyselect::ends_with("_acres")) |> 
    dplyr::rename_with(
      ~ gsub("_acres", "", .x)
      , tidyselect::ends_with("_acres")
    ) |> 
    dplyr::mutate(units = "ac")
) |> 
  dplyr::mutate(
    dplyr::across(
      -c(area_name,units)
      , ~ paste0(scales::comma(.x,accuracy=1)," ",units)
    )
  ) |> 
  dplyr::arrange(area_name,desc(units)) |> 
  dplyr::mutate(units = "") |> 
  dplyr::relocate(units,.after="area_name")
```


```{r, include=FALSE, eval=FALSE}
# tidyr::pivot_wider(
  #   names_from = crisis_strategy
  #   , values_from = c(area_ha,n)
  #   , names_glue = "{crisis_strategy}_{.value}"
  #   , values_fill = 0
  # ) |> 

  ggplot() + 
    geom_sf(
      data = USAboundaries::us_states(states = c(
          # usfs region 1-6 states
          "MT","WY","CO","NM","AZ","UT","ID","WA","OR","CA","NV"
          # , "KS","NE","SD","ND"
        )) |> 
        sf::st_transform(transform_crs)
      , fill = NA
      , color = "gray33"
    ) +
    geom_sf(aes(fill=crisis_strategy)) +
    geom_sf(data=wf_landscapes,fill=NA,color="black",lwd=0.6)+
    scale_fill_manual(values = c("All-Lands"="firebrick","USFS-Only"="orange3","No WCS Status"="gray")) +
    labs(
      fill = "Crisis Strategy\nCategory"
    ) +
    theme_light() +
    theme(
        legend.position = c(0.9,0.9) # "top"
        # , legend.direction = "horizontal"
        , legend.title = element_text(size = 8)
        , legend.text = element_text(size = 7)
        , axis.text = element_text(size=7)
      )
```


